I express my deep gratitude to my supervisors Prof. Nicolas Markey and Prof. Loic Helouet for all their time, advice and suggestions. I will always treasure our interactions and discussions, which helped me to shape not only my thesis but also my ideas and motivation for research. I hope to revisit and work with them in my near future. I would also like to thank all the professors and the PhD students of the SUMO group of INRIA Rennes for their heartfelt efforts and interactions of making my time pleasant and comfortable there. I would like to specially mention the name of Hugo Bazille for being an excellent friend and office-mate.
\vskip 0.2cm

I am deeply indebted to all the faculties of my college, Chennai Mathematical Institute for nurturing me for the last five years. Through their untiring efforts, guidance and inspirations they have continuously broadened my horizons, both as an academic and an individual. In particular, I would to like to take this moment to acknowledge the time and attention afforded to me by Prof. B. Srivathsan and Prof. Madhavan Mukund, who has put their utmost effort to make me fit in the research world. Through inspirations, encouragement and suggestions they have always motivated me towards my goal.
\vskip 0.2cm

I have now come to the juncture, where I must thank all my friends without whose support everything would have been so different. But, there are so many of you! Throughout this journey of 5 years, I met some wonderful seniors and friends who just made my world a bigger and happier place to live in. It is merely a short note of gratitude where I cannot mention all of your names but let me assure you that your influence has always been the light of my life to move forward.

Thank you Rajarshi Roy for all the moments, I will cherish them through out my lifetime. Thank you APNA Group for accepting me as one of you and sharing all the merriments. Thank you Vasudha Sharma, Kush Grover, Arijit Shaw for staying there in all of my highs and lows! A mere "APNA Game" will never be enough, this little piece of acknowledgement will never be enough! Thank you Utsab Ghosal to bear me so long as a roommate. Thank you Ananyo Kazi, Arghya Datta for all those memories. 

Shiuli Subhra Ghosh, thank you for everything and everything to come. You always stayed there and always understood.

"Sweet is the memory of distant friends! Like the mellow rays of departing sun, it falls tenderly, yet sadly on the heart"- Washington Irvin. I will miss you all!
\vskip 0.2cm

Lastly, the opportunity I hardly get, I would like to thank my parents Mr. Gora Raha \& Mrs. Rupali Raha for always supporting and believing in me. I will never fully comprehend all the things they endured to make all these possible. I am one of the luckiest brothers in the world to have a caring  sister like Sohini Raha; Thank you for being the most supporting person in my life even from distant apart.